---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# broom.helpers

<!-- badges: start -->
[![Lifecycle: maturing](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)
[![Travis build status](https://travis-ci.com/larmarange/broom.helpers.svg?branch=master)](https://travis-ci.com/larmarange/broom.helpers)
[![R build status](https://github.com/larmarange/broom.helpers/workflows/R-CMD-check/badge.svg)](https://github.com/larmarange/broom.helpers/actions)
[![Codecov test coverage](https://codecov.io/gh/larmarange/broom.helpers/branch/master/graph/badge.svg)](https://codecov.io/gh/larmarange/broom.helpers?branch=master)
[![CRAN status](https://www.r-pkg.org/badges/version/broom.helpers)](https://CRAN.R-project.org/package=broom.helpers)
<!-- badges: end -->

The broom.helpers package provides suite of functions to work with regression model `broom::tidy()` tibbles.
The suite includes functions to group regression model terms by variable, insert reference and header rows for categorical variables, add variable labels, and more.

## Installation

This package is still experimental and under development.

To install it for testing purpose, use:

``` r
devtools::install_github("larmarange/broom.helpers")
```

## Examples

```{r example}
library(broom.helpers)

# build regression model
lm(mpg ~ factor(cyl) + hp, mtcars) %>%
  # perform initial tidying of model
  tidy_and_attach() %>%
  # add reference row cyl
  tidy_add_reference_rows() %>%
  # add the cyl levels
  tidy_add_term_labels() %>%
  # remove intercept
  tidy_remove_intercept()
```

The package also includes a handy wrapper for the most commonly used functions.

```{r cars}
lm(mpg ~ factor(cyl) + hp, mtcars) %>%
  tidy_plus_plus()
```
